A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
intro edits

\begin{document}
\title{A Comparison of Parallel Graph Processing Benchmarks}
\author{Samuel D. Pollard \and Boyana Norris}
\institute{University of Oregon \\
	Eugene OR 97403, USA \\
	\email{spollard@cs.uoregon.edu} \\
	\email{norris@cs.uoregon.edu}
}
\maketitle
\begin{abstract}
The increasing popularity of large network analysis problems has led to the emergence of many parallel and distributed graph processing systems---one survey in 2014 identified over 80. Since then, the landscape has evolved; some packages have become inactive while more are being developed. Determining the best approach for a given problem is infeasible for most developers. To enable easy, rigorous, and repeatable comparison of the capabilities of such systems, we present an approach and associated software for analyzing the performance and scalability of parallel, open-source graph libraries. We demonstrate our approach on five graph frameworks: GraphMat, the Graph500, the Graph Algorithm Platform, GraphBIG, and PowerGraph using synthetic and real-world datasets. We examine previously overlooked aspects of parallel graph processing performance such as phases of execution and energy usage for three algorithms: breadth first search, single source shortest paths, and PageRank and compare our results to Graphalytics.
\end{abstract}

@@

%% What's the problem (motivation)
Our research is motivated by the current state of parallel graph processing. The most comprehensive survey, released in 2014, identified and taxonomized over 80 different parallel graph processing systems without even including domain specific languages \cite{Doekemeijer:2015:GPFSurvey}.

@@

Our contributions can be summarized as follows.
\begin{itemize}
	\item Automation of the installation, configuration, and dataset conversion to ensure the experiments execute in the same manner. Essentially, we provide a ``level playing field'' for graph algorithms.
	\item Comparison of algorithm runtime and scalability using a variety of data sets
	\item Comparison of our framework with the Graphalytics \cite{Capota:2015:Graphalytics} project
	\item Inspection of the source code of the surveyed parallel graph processing systems to ensure the same phases of execution are measured across differing execution and programming paradigms
	\item Provision of a experimental framework distinguishing between the data structure generation and algorithm execution phases of each system
	\item Analysis of energy consumption during the algorithm execution phase
\end{itemize}

@@

With a plugin to Graphalytics called Granula \cite{Ngai:2015:Granula} one can explicitly specify a performance model to analyze specific execution behavior such as the amount of communication or runtime of particular kernels of execution. This requires in-depth knowledge of the source code and execution model. Furthermore, creating such a model requires a high level of expertise with the given system and with Granula\footnote{An example of Granula can be seen at \url{https://github.com/tudelft-atlarge/graphalytics-platforms-graphx/tree/master/granula-model-graphx}}.

>>>>

\begin{document}
\title{A Comparison of Parallel Graph Processing Benchmarks}
\author{Samuel D. Pollard \and Boyana Norris}
\institute{University of Oregon \\
	Eugene OR 97403, USA \\
	\email{spollard@cs.uoregon.edu} \\
	\email{norris@cs.uoregon.edu}
}
\maketitle
\begin{abstract}
The rapidly growing number of large network analysis problems has led to the emergence of many parallel and distributed graph processing systems---one survey in 2014 identified over 80. Since then, the landscape has evolved; some packages have become inactive while more are being developed. Determining the best approach for a given problem is infeasible for most developers. To enable easy, rigorous, and repeatable comparison of the capabilities of such systems, we present an approach and associated software for analyzing the performance and scalability of parallel, open-source graph libraries. We demonstrate our approach on five graph frameworks: GraphMat, the Graph500, the Graph Algorithm Platform, GraphBIG, and PowerGraph using synthetic and real-world datasets. We examine previously overlooked aspects of parallel graph processing performance such as phases of execution and energy usage for three algorithms: breadth first search, single source shortest paths, and PageRank and compare our results to Graphalytics.
\end{abstract}

@@

%% What's the problem (motivation)
Our research is motivated by the current state of parallel graph processing. The most comprehensive survey, released in 2014, identified and categorized over 80 different parallel graph processing systems, without considering domain specific languages \cite{Doekemeijer:2015:GPFSurvey}.

@@

Our research contributions in this paper can be summarized as follows.
\begin{itemize}
	\item Automation of the installation, configuration, and dataset conversion to ensure the experiments execute in the same manner. Essentially, we provide a ``level playing field'' for graph algorithms.
	\item Comparison of algorithm runtime and scalability using a variety of data sets.
	\item Comparison of our framework with the Graphalytics \cite{Capota:2015:Graphalytics} project.
	\item Inspection of the source code of the surveyed parallel graph processing systems to ensure the same phases of execution are measured across differing execution and programming paradigms
	\item Provision of a experimental framework distinguishing between the data structure generation and algorithm execution phases of each system.
	\item Analysis of energy consumption during the algorithm execution phase.
\end{itemize}

@@

With a plugin to Graphalytics called Granula \cite{Ngai:2015:Granula}, one can explicitly specify a performance model to analyze specific execution behavior such as the amount of communication or runtime of particular kernels of execution. This requires in-depth knowledge of the source code and execution model. Furthermore, creating such a model requires a high level of expertise with the given system and with Granula\footnote{An example of Granula can be seen at \url{https://github.com/tudelft-atlarge/graphalytics-platforms-graphx/tree/master/granula-model-graphx}}.
